Declarative runtime reconfiguration of pulverised distributed systems \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-12 paper-2023-acsos-pulverization.tex
RW: Also mention service-based service composition

\newcommand{\ourframework}{Porbione}

@@

From the previous section,
we can identify two main phases in the pulverisation process:
\begin{enumerate*}[label=\it{(\roman*)}]
  \item the definition of the available devices and their capabilities; and
  \item the allocation of the pulverised components to them.
\end{enumerate*}
%
We decided to capture these phases into two distinct \acp{dsl}.

The first domain-specific language allows to define the system in terms of
\emph{devices}, \emph{components} and which \emph{capabilities} requires to be executed.
%
In this way, infrastructural and deployment aspects are abstracted, allowing the focus to be on functional aspects of the system.
%
The DSL enables the definition of the type of devices that took part in the system,
and for each device can be specified which components constitute it and where those component must run on (e.g. which host must execute the component).
%
The execution of a component is constrained to hosts with predetermined characteristics:
the framework models the constraint with the \texttt{Capability} concept,
namely the property that a host must to ``implement'' to run the component.
%
Different capabilities can be specified for each component to provide a more flexible and scalable deployment of the system.

@@

In our approach, the application partitioning into components is manually specified through a \ac{dsl}.
%
Therefore, it can be framed in the context of \emph{component-based software engineering},
 with ~\cite{vale2016component-based-se} providing a comprehensive review.
%
The specification or design of distributed systems
 may leverage
 component models~\cite{DBLP:journals/tse/CrnkovicSVC11},
 architectural description languages~\cite{DBLP:journals/tse/MedvidovicT00},
 or frameworks.
%

>>>>

\newcommand{\ourframework}{\texttt{pulse-refrakt}}

@@

From the previous section,
we can identify two main phases in the pulverisation process:
\begin{enumerate*}[label=\it{(\roman*)}]
  \item the definition of the available devices and their capabilities (infrastructure); and
  \item the allocation of the pulverised components to them (runtime).
\end{enumerate*}
%
We decided to capture these phases into two distinct \acp{dsl}.

The infrastructure \ac{dsl} captures the concepts of
\emph{logical device}, \emph{component}, \emph{capability}, and \emph{requirement}.
%
The DSL enables the definition of the type of devices that took part in the system,
and for each device can be specified which components constitute it and where those component must run on (e.g. which host must execute the component).
%
The execution of a component is constrained to hosts with predetermined characteristics:
the framework models the constraint with the \texttt{Capability} concept,
namely the property that a host must to ``implement'' to run the component.
%
Different capabilities can be specified for each component to provide a more flexible and scalable deployment of the system.

@@

In our approach, the application partitioning into components is manually specified through a \ac{dsl}.
%
Therefore, it can be framed in the context of \emph{component-based software engineering},
 with ~\cite{vale2016component-based-se} providing a comprehensive review.
%
The specification or design of distributed systems
 may leverage
 component models~\cite{DBLP:journals/tse/CrnkovicSVC11},
 architectural description languages~\cite{DBLP:journals/tse/MedvidovicT00},
 service-based compositions~\cite{DBLP:journals/csur/LemosDB16}, 
 or frameworks.
%
